---
title: "Untitled"
author: "ManBuXiaoCun"
date: '2022-04-22'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringi)
seq1 <- "ATGC-CG-"
reversed_string <- stri_reverse(seq1)
reversed_string
```
The origial seq is \
`r seq1`\
The reverse seq is \
`r reversed_string`


chartr() chartr translates each character in x that is specified in old to the corresponding character specified in new. 
Ideas from 
<https://stackoverflow.com/questions/20371854/complement-a-dna-sequence>
```{r}

# example to show function chartr()
# code from 
seq2 <- "ACCTGc-catGC--ATC"
seq2_complement <- chartr("acgtACGT-", "tgcaTGCA-", seq2)
seq2
seq2_complement

library(stringi)

rcseq <- function(nucSeq){
  return(stri_reverse(chartr("acgtACGTuU-", "tgcaTGCAaA-", nucSeq)))
  }

cseq <- function(nucSeq){
  return(chartr("acgtACGTuU-", "tgcaTGCAaA-", nucSeq))
  }

```


Eyeball check if a sequence contains illgal letters
```{r}
seqcontains <- function(myseq){
  result <- unique(strsplit(myseq,"")[[1]]) # [[1]] indexing is very important here 
  return(result)
}
```

gregexpr(pattern ='-',seq2) # change pattern = "change-pattern-here" send back where it is in the sequence/string. Here seq2 is the original sequence/string
```{r}
gregexpr(pattern ='-',seq2)
```



